---
title: "Iris Classification"
author: "Harmanpreet6351"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Iris Classification

## Loading required Libraries

```{r include = FALSE}
library(datasets)
library(GGally)
library(ggplot2)
library(e1071)
library(caret)
```

### About Data set

We are using Iris data set which comes with R dataset library

Viewing first 6 rows of data set

```{r}
head(iris)
```

Summarizing data

```{r}
summary(iris)
```

Visualizing

```{r}
ggpairs(iris[-5], mapping = aes(colour=iris$Species), progress = F)
```

### Splitting Dataset into train and test

```{r}
samp <- sample(nrow(iris), 0.75*nrow(iris))
train <- iris[samp,]
test <- iris[-samp,]
```

First 6 rows of Train data set

```{r}
head(train)
```

First 6 rows of Test data set

```{r}
head(test)
```

### Training model using Support Vector Machine

```{r}
model1 <- svm(Species ~ ., data = train)
pred1 <- predict(model1, test[-5])
confusionMatrix(pred1, test$Species)
```

### Training with Support Vector machine but only with Petal Length and Petal Width

```{r}
model2 <- svm(Species ~ Petal.Length + Petal.Width, data = train)
pred2 <- predict(model2, test[c(3,4)])
confusionMatrix(pred2, test$Species)
```

## A similar accuracy is achieved. Why?

From above analysis, it can been seen that petal length and petal width have high correlation and there we get a similar accuracy. Therefore, it can be concluded that **Petal Length and Petal Width are important features** as compared to Sepal Length and Sepal Width.

# Thank you.
